Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-10-17 workingdraft/draft.tex

Effective collector efficiency was found to decrease with increasing collector Reynolds number and collector density in nearly all cases \ref{figXXX}. One exception occurred at the lowest collector density ($\phi = 0.226\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 133$) had lower \%ECE than both the lower and higher $\Rey_c$ treatments. When compared to the other collector density treatments at this $\Rey_c = 133$ level, this treatment's \%ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment. Repeating the suspended sediment experiment for this combination of parameter values yielded a \%ECE value very close to the estimate from the original experiment.

Monte Carlo analysis determined that there is a significant negative relationship between \%ECE and collector density for the low ($\Rey_c = 66$) and high ($\Rey_c = 200$) collector Reynolds number treatments, but the trend was insignificant for the intermediate ($\Rey_c = 133$) treatment \ref{figYYYa}. This approach also found a significant negative relationship between \%ECE and $\Rey_c$ for the low ($\phi = 0.226\%$) and high ($\phi = 1.17\%$) collector density treatments, but an insignificant trend for the intermediate ($\phi = 0.650\%$) collector density treatment \ref{figYYYb}. Leaving out the insignificant relationships, the two relationships between \%ECE and collector density were considerably more significant than those between \%ECE and Reynolds number.

@@

\begin{table}[H]
\caption{Turbulence and flow characteristics for all collector solid volume fraction ($\phi$) and $\Rey_c$ treatments, including the control (zero-collector) treatments for reference}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{>{\bfseries}r>{\bfseries}rrrr}
\toprule
\textbf{$\phi$}&\textbf{$\Rey_c$}&\textbf{Turbulent Kinetic Energy (\SI{}{\metre^2/\second^2})}&\textbf{Bed Shear Stress (\SI{}{\pascal})}&\textbf{Longitudinal Velocity (\SI{}{\centi\metre/\second})}\\
\midrule
Control &   67  & \num{2.48d-6}&\num{-5.52d-4}&   2.03\\
        &   134 & \num{2.98d-6}&\num{ 3.17d-3}&   4.10\\
        &   200 & \num{3.37d-6}&\num{ 5.13d-3}&   6.24\\
\midrule
0.226\% &   67  & \num{1.23d-6}&\num{-2.95d-5}&   1.87\\
        &   134 & \num{5.26d-6}&\num{-1.39d-4}&   3.68\\
        &   200 & \num{1.22d-5}&\num{ 1.87d-2}&   5.65\\
\midrule
0.650\% &   67  & \num{9.13d-6}&\num{ 9.62d-4}&   1.39\\
        &   134 & \num{3.59d-5}&\num{ 1.20d-3}&   3.01\\
        &   200 & \num{5.96d-5}&\num{ 6.52d-4}&   4.70\\
\midrule
1.17\%  &   67  & \num{1.11d-5}&\num{ 4.47d-4}&   1.76\\
        &   134 & \num{2.98d-5}&\num{ 1.36d-3}&   4.22\\
        &   200 & \num{5.44d-5}&\num{ 2.44d-3}&   5.41\\
\bottomrule
\end{tabular}
\end{table}

>>>>

Effective collector efficiency was found to decrease with increasing collector Reynolds number and collector density in nearly all cases \ref{figXXX}. One exception occurred at the lowest collector density ($\phi = 0.226\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 133$) had lower ECE than both the lower and higher $\Rey_c$ treatments. When compared to the other collector density treatments with the same $\Rey_c$ value, this low collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment. Repeating the suspended sediment experiment for this combination of parameter values yielded a ECE value very close to the estimate from the original experiment.

Monte Carlo analysis determined that there is a significant negative relationship between ECE and collector density for the low (p = 0.004) and high (p = 0.019) $\Rey_c$ treatments, but no significant effect was detected (p > 0.05) for the intermediate treatment (Figure \ref{fig:monte}a). This approach also found a significant negative relationship between ECE and $\Rey_c$ for the low (p = 0.026) and high (p = 0.046) collector density treatments, but an insignificant (p > 0.05) trend for the intermediate collector density treatment (Figure \ref{fig:monte}b).

\begin{figure}[H]
\centering
\includegraphics{../pics/montecarlo.png}
\caption{Effect size estimates resulting from Monte Carlo regression analysis. Error bars represent 95\% confidence intervals. Asterisks mark (\textbf{a}) Estimates of the effect of log-transformed collector solid volume fraction ($\beta_{\log(\phi)}$) on ECE, stratified by $\Rey_c$. (\textbf{b}) Estimates of the effect of log-transformed $\Rey_c$ ($\beta_{\log(\Rey)}$) on ECE, stratified by solid volume fraction.}
\label{fig:monte}
\end{figure}

@@

\begin{table}[H]
\caption{Turbulence and flow characteristics for all collector solid volume fraction ($\phi$) and $\Rey_c$ treatments, including the control (zero-collector) treatments for reference}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{>{\bfseries}r>{\bfseries}rrr}
\toprule
\textbf{$\phi$}&\textbf{$\Rey_c$}&\textbf{Turbulent Kinetic Energy (\SI{}{\metre^2/\second^2})}&\textbf{Bed Shear Stress (\SI{}{\pascal})}\\
\midrule
Control &   67  & \num{2.48d-6}&\num{-5.52d-4}\\
        &   134 & \num{2.98d-6}&\num{ 3.17d-3}\\
        &   200 & \num{3.37d-6}&\num{ 5.13d-3}\\
\midrule
0.226\% &   67  & \num{1.23d-6}&\num{-2.95d-5}\\
        &   134 & \num{5.26d-6}&\num{-1.39d-4}\\
        &   200 & \num{1.22d-5}&\num{ 1.87d-2}\\
\midrule
0.650\% &   67  & \num{9.13d-6}&\num{ 9.62d-4}\\
        &   134 & \num{3.59d-5}&\num{ 1.20d-3}\\
        &   200 & \num{5.96d-5}&\num{ 6.52d-4}\\
\midrule
1.17\%  &   67  & \num{1.11d-5}&\num{ 4.47d-4}\\
        &   134 & \num{2.98d-5}&\num{ 1.36d-3}\\
        &   200 & \num{5.44d-5}&\num{ 2.44d-3}\\
\bottomrule
\end{tabular}
\end{table}
